SAT Competition 2020\tnoteref{title}

### 2021-01-08 paper/main.tex
one sentence

In this section, we provide additional views on the Main track results,
in particular focusing on metrics which help to highlight strengths

>>>>

In this section, we provide additional views on the Main track results,
focusing on metrics complementing the PAR-2 score, 
which we used for ranking the solvers in the actual competition.
